---
output:
  rmarkdown::pdf_document:
    template: template.tex
    keep_tex: true
geometry: margin=2cm
---

```{r echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)

entries <- read.csv("entries.csv", sep = ";")
```

\textbf{\huge{HELLO}}
\vspace{0.2cm}

Luxembourg Institute of Socio-Economic Research 

11, Porte des Sciences \hfill \href{mailto:etienne.bacher@liser.lu}{\texttt{etienne.bacher@liser.lu}}

L-4366 Esch-sur-Alzette/Belval, Luxembourg \hfill \href{https://www.etiennebacher.com/}{\texttt{www.etiennebacher.com}}


# Education

```{r, results='asis'}
entries_educ <- entries %>%
  filter(type == "education")

for (i in 1:nrow(entries_educ)) {
  tmp <- entries_educ[i, ] %>% 
    select(where(~ .x != ""))
  tmp_details <- tmp[which(grepl("detail", names(tmp)))]
  cat('
::: {.cols data-latex=""}
::: {.col data-latex="{0.15\\textwidth}"}\n',
tmp$year1, " -- ", tmp$year2,
'
:::
::: {.col data-latex="{0.03\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.55\\textwidth}"}\n',
tmp$title,
'
:::
::: {.col data-latex="{0.25\\textwidth}"}
::: {.flushright data-latex=""}\n',
"\\textcolor{mygray}{", tmp$institution, ", ", tmp$place, "}",
'
:::
:::
:::',
sep = "")
if (length(tmp_details > 0)) {
  cat(
'
::: {.cols data-latex=""}
::: {.col data-latex="{0.15\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.03\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.8\\textwidth}"}\n',
paste("* ", tmp_details, collapse = "\n"),
'
:::
:::
',
sep = ""
  )}
}
```

# Professional experience

```{r, results='asis'}
entries_pro <- entries %>%
  filter(type == "professional_experience")

for (i in 1:nrow(entries_pro)) {
  
  tmp <- entries_pro[i, ] %>% 
    select(where(~ .x != ""))
  
  tmp_details <- tmp[which(grepl("detail", names(tmp)))]
  
  if (tmp$year1 == as.numeric(substr(tmp$year2, 1, 4))) {
    time <- tmp$year2 # year2 to get the duration too
  } else { 
    time <- paste0(tmp$year1, " -- ", tmp$year2)
  }
  
  cat('
::: {.cols data-latex=""}
::: {.col data-latex="{0.15\\textwidth}"}\n',
time,
'
:::
::: {.col data-latex="{0.03\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.55\\textwidth}"}\n',
tmp$title,
'
:::
::: {.col data-latex="{0.25\\textwidth}"}
::: {.flushright data-latex=""}\n',
"\\textcolor{mygray}{", tmp$institution, ", ", tmp$place, "}",
'
:::
:::
:::
::: {.cols data-latex=""}
::: {.col data-latex="{0.15\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.03\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.8\\textwidth}"}\n',

paste("* ", tmp_details, collapse = "\n"),
'
:::
:::
',
sep = ""
  )
}
```


# Conferences

```{r, results='asis'}
entries_conf <- entries %>%
  filter(type == "conference")

for (i in unique(entries_conf$year1)) {
  tmp <- entries_conf %>% 
    select(where(~ .x != "")) %>% 
    filter(year1 == i)

  cat(
    "**", tmp$year1, "**: ", paste0(tmp$title, " (", tmp$detail1, ")"),
    sep = ""
  )
}
```


# Computer skills

**Advanced:** R

**Intermediate:** Stata, LaTeX, HTML, CSS

**Basic:** Matlab, GAMS

**Misc:** Ubuntu


# Languages

French (native), English (fluent), Spanish (basic)



\vspace{2cm}


```{r}
Sys.setlocale("LC_TIME", "English") |> 
  invisible() # for date below
```

\begin{center}
CV last updated on `r format(Sys.Date(), format="%B %d, %Y")`
\end{center}