---
output:
  rmarkdown::pdf_document:
    template: template.tex
    keep_tex: true
geometry: margin=2cm
---

```{r echo = FALSE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)

entries <- readr::read_csv("entries.csv")
```

\textbf{\huge{Etienne Bacher}}
\vspace{0.2cm}

Luxembourg Institute of Socio-Economic Research \hfill \href{mailto:etienne.bacher@liser.lu}{\texttt{etienne.bacher@liser.lu}}

11, Porte des Sciences \hfill \href{https://www.etiennebacher.com/}{\texttt{www.etiennebacher.com}}

L-4366 Esch-sur-Alzette/Belval, Luxembourg \hfill \href{https://github.com/etiennebacher/}{\texttt{github.com/etiennebacher}}


# Education

```{r, results='asis'}
entries_educ <- entries %>%
  filter(type == "education")

for (i in 1:nrow(entries_educ)) {
  tmp <- entries_educ[i, ] %>% 
    select(where(~ .x != "" & !is.na(.x)))
  tmp_details <- tmp[which(grepl("detail", names(tmp)))]
  cat('
::: {.cols data-latex=""}
::: {.col data-latex="{0.15\\textwidth}"}\n',
tmp$year1, " -- ", tmp$year2,
'
:::
::: {.col data-latex="{0.03\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.55\\textwidth}"}\n',
tmp$title,
'
:::
::: {.col data-latex="{0.25\\textwidth}"}
::: {.flushright data-latex=""}\n',
"\\textcolor{mygray}{", tmp$institution, ", ", tmp$place, "}",
'
:::
:::
:::',
sep = "")
if (length(tmp_details > 0)) {
  cat(
'
::: {.cols data-latex=""}
::: {.col data-latex="{0.15\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.03\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.8\\textwidth}"}\n',
paste("* ", tmp_details, collapse = "\n"),
'
:::
:::
',
sep = ""
  )}
}
```

# Professional experience

```{r, results='asis'}
entries_pro <- entries %>%
  filter(type == "professional_experience")

for (i in 1:nrow(entries_pro)) {
  
  tmp <- entries_pro[i, ] %>% 
    select(where(~ .x != "" & !is.na(.x)))
  
  tmp_details <- tmp[which(grepl("detail", names(tmp)))]
  
  if (tmp$year1 == as.numeric(substr(tmp$year2, 1, 4))) {
    time <- tmp$year2 # year2 to get the duration too
  } else { 
    time <- paste0(tmp$year1, " -- ", tmp$year2)
  }
  
  cat('
::: {.cols data-latex=""}
::: {.col data-latex="{0.15\\textwidth}"}\n',
time,
'
:::
::: {.col data-latex="{0.03\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.55\\textwidth}"}\n',
tmp$title,
'
:::
::: {.col data-latex="{0.25\\textwidth}"}
::: {.flushright data-latex=""}\n',
"\\textcolor{mygray}{", tmp$institution, ", ", tmp$place, "}",
'
:::
:::
:::
::: {.cols data-latex=""}
::: {.col data-latex="{0.15\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.03\\textwidth}"}
\\ 
:::
::: {.col data-latex="{0.8\\textwidth}"}\n',

paste("* ", tmp_details, collapse = "\n"),
'
:::
:::
',
sep = ""
  )
}
```

# Works in progress

**The vicious circle of xenophobia**, *with Michel Beine and Hillel Rapoport*

**Populist leaders and international migration**

# Publications

1. **Bacher, E.**, Herrera-Rodriguez, M., Marino Fages, D., Stips, F., (2023). A Replication of Jones & Marinescu (2022), *I4R Discussion Paper Series* n°80 

2. Patil, I., Makowski, D., Ben-Shachar, M. S., Wiernik, B., **Bacher, E.**, Lüdecke, D., (2022). datawizard: An R Package for Easy Data Preparation and Statistical Transformations. *Journal of Open Source Software*, 7(78), 4684, https://doi.org/10.21105/joss.04684


# Conferences & workshops

```{r, results='asis'}
entries_conf <- entries %>%
  filter(type == "conference")

for (i in rev(unique(entries_conf$year1))) {
  tmp <- entries_conf %>% 
    filter(year1 == i) %>% 
    mutate(detail1 = ifelse(!is.na(detail1), paste0(" (", detail1, ")\n\n"), "\n\n"))

  tmp$detail1 <- gsub("\\n", "", tmp$detail1)
  
  cat(
    "\n\n**", unique(tmp$year1), "**: ", paste0(tmp$title, tmp$detail1, collapse = ", "),
    sep = ""
  )
}
```

# Relevant activities

Co-organizer of the [Economics of Migration Junior seminar](https://sites.google.com/view/the-economics-of-migration)

# Teaching

Teaching Assistant:

* International Economics (Fall 2021, 2022, 2023), *3rd year Bachelor* (Prof. Michel Beine)

Workshop:

* Webscraping with RSelenium


# Computer skills

**Advanced:** R

  * Member of the [easystats team](https://github.com/easystats/)
  
  * Author or maintainer of several R packages: [altdoc](https://github.com/etiennebacher/altdoc), [conductor](https://github.com/etiennebacher/conductor), [datawizard](https://easystats.github.io/datawizard/), [prompter](https://github.com/etiennebacher/prompter), [tidypolars](https://tidypolars.etiennebacher.com/)
  
  * Significant contributions to several R packages: [marginaleffects](https://vincentarelbundock.github.io/marginaleffects/), [polars](https://rpolars.github.io/), [poorman](https://nathaneastwood.github.io/poorman/), [WDI](https://vincentarelbundock.github.io/WDI/).

**Intermediate:** Stata, LaTeX, HTML, CSS

**Basic:** Matlab, JavaScript, GAMS

**Misc:** Ubuntu/Linux


# Languages

French (native), English (fluent), Spanish (basic)

